cluster-utils Analysis

### 2024-08-28 analyses/cluster-utils/notebook-template.Rmd
add module with renv and some readme filled in

---
title: "ewings-cell-type Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "ewings-cell-type")
```

>>>>

---
title: "cluster-utils Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "cluster-utils")
```
